Incorporating periodic variability in hidden Markov models for animal movement

### 2016-02-29 paper3.Rnw
fix table caption
lengend change?

<<state_plots cat15, warning=FALSE, message=FALSE, echo=FALSE, fig.cap="States">>=
load("cat15sumdat.RData")
temp5 <- tail(getpars(fitsin5s),10)
temp6 <- tail(getpars(fithomo6s),12)
dat1 <- data.frame(log_mean=temp5[c(1,3,5,7,9)],
                     log_sd=temp5[c(2,4,6,8,10)], Model="HMM") 
dat2 <- data.frame(log_mean=temp6[c(1,3,5,7,9,11)],
                     log_sd=temp6[c(2,4,6,8,10,12)],Model="HMM + TH(sin)") 
dat1 <- dat1[order(dat1$log_mean),]
dat2 <- dat2[order(dat2$log_mean),]

@@

\begin{table}[]
\centering
\caption{Number of Parameters for each model type. 
\label{Cat-ID}
\begin{tabular}{cccc}
 Type & Model  & Number of States & Number of Parameters  \\
  FMM & FMM & 3 & 9    \\
  FMM & FMM & 4 & 12    \\
  FMM & FMM & 5 & 15   \\
  FMM & FMM & 6 & 18  \\
  FMM + TH & FMM + TH (Sin)  & 3 & 15    \\
  FMM + TH & FMM + TH (Sin)  & 4 & 20    \\
  FMM + TH & FMM + TH (Sin)  & 5 & 25    \\
  FMM + TH & FMM + TH (Sin)  & 6 & 30    \\
  HMM & HMM & 3 & 18    \\
  HMM & HMM & 4 & 28    \\
  HMM & HMM & 5 & 40   \\
  HMM & HMM & 6 & 54  \\
  HMM + TH & HMM + TH (Block)  & 3 & 36    \\
  HMM + TH & HMM + TH (Block)  & 4 & 60    \\
  HMM + TH & HMM + TH (Block)  & 5 & 90    \\
  HMM + TH & HMM + TH (Block)  & 6 & 126    \\
  HMM + TH & HMM + TH (Quad)  & 3 & 36    \\
  HMM + TH & HMM + TH (Quad)  & 4 & 60    \\
  HMM + TH & HMM + TH (Quad)  & 5 & 90    \\
  HMM + TH & HMM + TH (Quad)  & 6 & 126    \\
  HMM + TH & HMM + TH (Sin)  & 3 & 36    \\
  HMM + TH & HMM + TH (Sin)  & 4 & 60    \\
  HMM + TH & HMM + TH (Sin)  & 5 & 90    \\
  HMM + TH & HMM + TH (Sin)  & 6 & 126    \\
  HMM + TH & HMM + TH (Hourly)  & 3 & 225    \\
  HMM + TH & HMM + TH (Hourly)  & 4 & 396    
\end{tabular}
\end{table}

>>>>

<<state_plots cat15, warning=FALSE, message=FALSE, echo=FALSE, fig.cap="States">>=
load("cat15sumdat.RData")
temp5 <- tail(getpars(fitsin5s),10)
temp6 <- tail(getpars(fithomo6s),12)
dat1 <- data.frame(log_mean=temp5[c(1,3,5,7,9)],
                     log_sd=temp5[c(2,4,6,8,10)], Model="HMM + TH(sin)") 
dat2 <- data.frame(log_mean=temp6[c(1,3,5,7,9,11)],
                     log_sd=temp6[c(2,4,6,8,10,12)],Model="HMM") 
dat1 <- dat1[order(dat1$log_mean),]
dat2 <- dat2[order(dat2$log_mean),]

@@

\begin{table}[]
\centering
\caption{Number of Parameters for each model type.}
\label{Cat-ID}
\begin{tabular}{cccc}
 Type & Model  & Number of States & Number of Parameters  \\
  FMM & FMM & 3 & 9    \\
  FMM & FMM & 4 & 12    \\
  FMM & FMM & 5 & 15   \\
  FMM & FMM & 6 & 18  \\
  FMM + TH & FMM + TH (Sin)  & 3 & 15    \\
  FMM + TH & FMM + TH (Sin)  & 4 & 20    \\
  FMM + TH & FMM + TH (Sin)  & 5 & 25    \\
  FMM + TH & FMM + TH (Sin)  & 6 & 30    \\
  HMM & HMM & 3 & 18    \\
  HMM & HMM & 4 & 28    \\
  HMM & HMM & 5 & 40   \\
  HMM & HMM & 6 & 54  \\
  HMM + TH & HMM + TH (Block)  & 3 & 36    \\
  HMM + TH & HMM + TH (Block)  & 4 & 60    \\
  HMM + TH & HMM + TH (Block)  & 5 & 90    \\
  HMM + TH & HMM + TH (Block)  & 6 & 126    \\
  HMM + TH & HMM + TH (Quad)  & 3 & 36    \\
  HMM + TH & HMM + TH (Quad)  & 4 & 60    \\
  HMM + TH & HMM + TH (Quad)  & 5 & 90    \\
  HMM + TH & HMM + TH (Quad)  & 6 & 126    \\
  HMM + TH & HMM + TH (Sin)  & 3 & 36    \\
  HMM + TH & HMM + TH (Sin)  & 4 & 60    \\
  HMM + TH & HMM + TH (Sin)  & 5 & 90    \\
  HMM + TH & HMM + TH (Sin)  & 6 & 126    \\
  HMM + TH & HMM + TH (Hourly)  & 3 & 225    \\
  HMM + TH & HMM + TH (Hourly)  & 4 & 396    
\end{tabular}
\end{table}
